We set out with the purpose of answering a list of questions, or at least YY\\

Q0 - Mimimale\\
Q1 - Are BC/IC sufficient?\\
Q2 - Given a bottom-up, full scale model, what can we say re: domain-interactions\\
\\\\
Result 1: \
Result 2a: Comparison between Silico mutants and Vivo mutants\\
Result 2a: Comparison between Silico mutants and Silico optimal (remember to include PCP-orientation)\\

----------------------

Through examining the biology of the cell, specifics of gastrulation, and the literature on existing in silico solution, we proposed a biologically sensible, simple computer model of a single cell. Using existing data of the genetic expression of the fruit fly embryo, the base for the gastrulation was [made] and condensed to only a handful of parameters. 
The model was initially validated by large-scale visual analysis, of the timing, YY and . By recognizing a number of key dynamic events in the [embryogenesis], the morphogenetic timeline was [exhaustively] compared to the very well studied gastrulation. We believe to have found a phenomenological overlap UUU. 
When the [visual validity] of the model was [understood], a number of numerical metrics was devices so as to quantify the [agreement] between simulation and reality. These metrics were tested .
Finally, after as UU, 

We fo



When looking at morphogenesis, you are certain at encountering the gastrulation of the fruit fly.

As we have studied Drosophila Melongaster, a self-perpetuating effect has brought it to be the de-facto model organism for much of the 

We wanted to probe the feasibility of [recuperating] using a point-based simulation with minimal rule-set. We have kept every interaction as biologically defensible as possible, keeping in mind that most coordinated efforts in nature are emergent -- with all(/most?) large-scale information sharing contained in the initial conditions.
After [trusting] the phenomenological validity of our simulation, we . Checking its stability under perturbations in parameters and [YYY].\\

For the qualitative and quantitative comparisons between silico and vivo we found the following.

Folds on the top (dorsal) side would be a welcome addition. The literature agrees \reph\todo{Link to the paper where it show it happens under stress}. Cells shape change for added motion on the bottom. We saw, when trying to have more horizontal pressure come from the \vf{ventral furrow}. Active intercalations (as described in Section \ref{sec:germ-band}) are simply not enough. This, we found out, was also corroborated by the literature \cite{detder}.

Explicit timing does not seem needed!

Using our novel modeling approach we have found the interplay between seemingly disparate biomechanical events to be [vital]. This is   unsurprisingly as the different   

The fractal-like YYY of emergence across multiple [phsyical scales] is defining for natural phenomena.

Turing


\textbf{We are in a way the first who can simulate the posterior invagination (PMG) \pmg{A3} as this requires both successful modelling of \vf{A1} and \gb{A2}. Each of which has had multiple YYY before, but never in a way where combining them was possible}


\section{Questions}
\todo{Give me all the questions again}
Q0 - Mimimale\\
Q1 - Are BC/IC sufficient?\\
Q2 - Given a bottom-up, full scale model, what can we say re: domain-interactions\\
\\\\
Result 1: \
Result 2a: Comparison between Silico mutants and Vivo mutants\\
Result 2a: Comparison between Silico mutants and Silico optimal (remember to include PCP-orientation)\\

\section{Answers}
\begin{itemize}
    \item Polarizations and cell-interactions only set from biologically founded initial conditions.
    \item No  timing
    \item Stable under perturbations
    \item With a p-value of 
\end{itemize}

While looking at the [small parts] in many cases can lead to crudely reductionist conclusions, it is sometimes the only obvious.

We have seen that even if many biological systems are "more than than the sum of its parts", having a model for the parts can allow for .

We have shown that complex time-[something] of events can arise from the physically simple interactions with boundary conditions and mechanical feedback-loops.

\textbf{We are in a way the first who can simulate the posterior invagination (PMG) \pmg{A3} as this requires both successful modelling of \vf{A1} and \gb{A2}. Each of which has had multiple YYY before, but never in a way where combining them was possible}\\\\


\textbf{List of things that we know we have not taken into account but very likely could have been helpful}:
Cell shape change, Dorsal folds, Cephalic fold.

\textbf{Comparisons to data}\\
We have found through multiple comparisons, how our simulation is recapitulating the dynamics.

The movement vectors, timing, strain-distribution over time and rosettes all had clear relations[?] to reality while also showing the different shortcomings where our methodology could be improved.
\textbf{Further work}

We have identified the possibility of cell shape change (i.e. anisotropic relaxation distances in relation to external pressure) to be the most promising next step. Some work was already put into this witout anything fruitful. Other potential expansions on the model would be for the dorsal and cephalic folds to buckle under pressure. Also adding in the in-plane proliferation in the cephalic region. This was implemented, but removed for simplicity.

\textbf{Combinations}
We have seen that every part of the simulated embryo was necessary for successful gastrulation. 
While both our model and nature is stable to noise and YYY, the environment, boundary conditions and initial conditions are vital for defining YYY

\textbf{closing remarks}
Turing showed that simple interplay between chemicals can create arbitrarily complex biopatterning that can serve as a blueprint. We have taken a step in the direction of showing how a combination between minimal environmental information and simple rules for the interplay between individual cells can lead to the creation of physical form. \todo{rephrase}\\


\textit{axiomatic}dk